AggregateCounts

### 2021-09-04 R/AggregateCounts.Rmd
Re-ran it from scratch and fixed some grouping errors

```{r aggregate wrangling and overview plots}
#Statistics from all aggregates
#Get aggregate summary per sample
aggregateListSummaryReplicate<-aggregateList%>% group_by(SampleCode, Species,SaStrain, Strain, Culture,TimePoint, Condition, Replicate,Region) %>% 
  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass)

#Get aggregate Summary per condition
aggregateListSummaryCondNoRegion<-aggregateListSummaryReplicate %>% group_by(Species,SaStrain, Strain, Culture,TimePoint, Condition) %>% 
  summarise(meanAggs= mean(Aggs), meanBiomassLog = mean(log10(biomass)), SEBiomassLog = std.error((log10(biomass))), meanAggSize = mean(meanAggSize), seAggSize = std.error(meanAggSize))%>%  mutate(meanBiomass =  meanBiomassLog^10, SEBiomass = SEBiomassLog^10)

#Get aggregate Summary per condition and region
aggregateListSummaryCondition<-aggregateListSummaryReplicate %>% group_by(Species, SaStrain,Strain, Culture,TimePoint, Condition, Region) %>% 
  summarise(meanAggs= mean(Aggs), meanBiomassLog = mean(log10(biomass)), SEBiomassLog = std.error((log10(biomass))), meanAggSize = mean(meanAggSize), seAggSize = std.error(meanAggSize))%>%  mutate(meanBiomass =  meanBiomassLog^10, SEBiomass = SEBiomassLog^10)

#Plot agg summary per sample
#####
ggplot()+ 
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Strain,shape = "MeanSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Strain, shape = "MaxSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Strain, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(Species~Culture, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  scale_color_brewer(palette = "Set1")+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
#####
#Plot only biomass per Sample
#####
PlotBiomasPerSample<-function(df){
ggplot()+ 
    #this is for multiple conditions
  #geom_point(data = df, aes(x = Strain, y= biomass, shape = Region, color = Culture),size = 3, position = position_dodge(width = .6))+
  geom_point(data = df, aes(x = Culture, y= biomass, color= Species, shape = Region),size = 3, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
      #this is for multiple conditions  
    #facet_grid(Species~TimePoint, scales = "free", space = "free") +
    #this is for only one mutant
    facet_grid(.~TimePoint, scales = "free", space = "free") +
  ggtitle('Total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(1, 2,0))+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

@@

#There are two ways to normalize the Bin Frequncy and Bin Biomass, per condition and per sample, so I'll do both
#First per replicate:
#####
HistReplicate<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ "(.5, 5]",
                        Size<= 10 ~ "(5, 10]",
                        Size<= 100    ~ "(10, 100]",
                        Size<= 1000   ~ "(100, 1000]",
                        Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
  group_by(SampleCode)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% 
  group_by(SampleCode, LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

@@

#This is weird, but I want to have the histogram above with all the data, and the one below with only the bins
HistReplicateSummary<-HistReplicate %>% 
  group_by(Species,Culture,SaStrain, Strain,Region,Condition,TimePoint, Replicate,SampleCode, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%
  unique()%>%ungroup() %>%  group_by(Species,Strain, SaStrain,Culture,Condition,TimePoint, Replicate, SampleCode) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
#####
#Now per condition. The difference is int the "group_by" part
#####
HistCondition<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ "(.5, 5]",
                        Size<= 10 ~ "(5, 10]",
                        Size<= 100    ~ "(10, 100]",
                        Size<= 1000   ~ "(100, 1000]",
                        Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
  group_by(Species,Condition,TimePoint)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>%
  group_by(Species, Condition,TimePoint,LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)
HistCondition$LogBin <- factor(HistCondition$LogBin, levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")")),labels = c(levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")"))))

#Summary data frame
HistConditionSummary<-HistCondition %>%
  group_by(Species,Culture,SaStrain, Strain, Condition,TimePoint,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
  summarize() %>% unique()%>%ungroup() %>%
  group_by(Species,Culture,Strain,SaStrain, Condition,TimePoint) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
#####

#Now per condition including region. The difference is int the "group_by" part
#####
HistConditionRegin<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ "(.5, 5]",
                        Size<= 10 ~ "(5, 10]",
                        Size<= 100    ~ "(10, 100]",
                        Size<= 1000   ~ "(100, 1000]",
                        Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
  group_by(Species,Condition,TimePoint, Region)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>%
  group_by(Species, Condition,TimePoint, Region,LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

HistConditionRegin$LogBin <- factor(HistConditionRegin$LogBin, levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")")),labels = c(levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")"))))

#Summary data frame
HistCondRegionSum<-HistConditionRegin %>%
  group_by(Species,Culture,SaStrain, Strain, Condition,TimePoint, Region,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
  summarize() %>% unique()%>%ungroup() %>%
  group_by(Species,Culture,Strain,SaStrain, Condition,TimePoint, Region) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
#####

#Plot Normalized Frequency
#this isn't useful as the normalized Frequency changes with replicate, so it's better to pool all samples together
PlotHistSum<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4")%>% filter(Species == species),
                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4")%>% filter(Species == species),
               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=3, position = position_dodge(width = .75) )+
    geom_point(data = cond.df%>% filter(TimePoint=="Day 4") %>% filter(Species == species),
               aes(x=as.factor(LogBin),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~Species)+
    scale_shape_manual(values=c(16, 1))+
    ggtitle(title)+
    labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotHistSum(HistReplicateSummary,HistConditionSummary,HistCondRegionSum,"NormalizedFrequency", "Normalized Frequency all sizes", "S. aureus")

@@

PlotHistSum(HistReplicateSummary,HistCondRegionSum,HistConditionSummary,"NormalizedBiomass", "Normalized Biomass all sizes")

#Plot normalized Biomass per sample
##Pa
PlotHistRepBioTrend<-function(rep.df,species){
ggplot()+
    geom_line(data = rep.df %>% filter(Species==species),aes(x=as.factor(LogBin),y=NormalizedBiomass, color = Replicate, group = Replicate ),size=1)+
    guides(color = FALSE)+
    facet_grid(Condition~TimePoint)+
    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    ggtitle(paste('Normalized Biomass per Sample', species))+
    theme_cowplot()+
    scale_colour_grey()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5)) }
PlotHistRepBioTrend(HistReplicateSummary, "P. aeruginosa")
PlotHistRepBioTrend(HistReplicateSummary, "S. aureus")

#####
#Now only aggregates 5 microns or larger

@@

#####

#Planktonic vs aggregates
#####
#Add agregation value to the dataframe 
##Normalize using replicates
HistReplicate<-HistReplicate %>%  mutate(Aggregation = if_else(LogBin == "(.5, 5]" ,"Planktonic", "Aggregate")) %>%
  group_by(Species,SampleCode, Aggregation)%>% 
  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
#Collapse to only values per replicate
plankAggHistRep<-HistReplicate %>% 
  group_by(Species,Culture,Condition,Strain,TimePoint, Replicate, SaStrain, Region, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% 
  summarize() %>%  unique()%>%ungroup() %>%  
  group_by(Species,Culture,Condition,Strain,TimePoint, Replicate, SaStrain, Region) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))

##Normalize using Condition and region
HistConditionRegin<-HistConditionRegin %>%  mutate(Aggregation = if_else(LogBin == "(.5, 5]", "Planktonic", "Aggregate")) %>%
  group_by(Species,Culture,Condition,Strain, TimePoint,Region, SaStrain, Aggregation)%>% 
  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
#Collapse to only values per replicate
plankAggHistCondReg<-HistConditionRegin %>% 
  group_by(Species,Culture,Condition,SaStrain, Region,Strain,TimePoint, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>%
  summarize() %>%  unique()%>%ungroup() %>%
  group_by(Species,Culture,Condition,SaStrain, Region,Strain,TimePoint) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))

##Normalize using Condition 
HistCondition<-HistCondition %>%  mutate(Aggregation = if_else(LogBin == "(.5, 5]", "Planktonic", "Aggregate")) %>%
  group_by(Species,Culture,Condition,SaStrain, TimePoint,Strain, Aggregation)%>% 
  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
#Collapse to only values per replicate
plankAggHistCond<-HistCondition %>% 
  group_by(Species,Culture,Condition,Strain,SaStrain,TimePoint, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>%
  summarize() %>%  unique()%>%ungroup() %>%  
  group_by(Species,Culture,Condition,Strain,SaStrain,TimePoint) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))

>>>>

```{r aggregate wrangling}
#Statistics from all aggregates
#Get aggregate summary per sample
aggregateListSummaryReplicate<-aggregateList%>% group_by(SampleCode,Species,SaStrain,Strain,Culture,TimePoint,Condition,Replicate,Region) %>% 
  summarise(Aggs = n(), Biomass = sum(Size), MeanAggSize = mean(Size), SEAggSize = std.error(Size), MaxSize = max(Size), MinSize = min(Size)) %>%
  ungroup() %>% mutate(RatioMaxTotal = MaxSize/Biomass)

#Get aggregate Summary per condition
aggregateListSummaryCondNoRegion<-aggregateListSummaryReplicate %>% group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition) %>% 
  summarise(MeanAggs= mean(Aggs), MeanBiomassLog = mean(log10(Biomass)), SEBiomassLog = std.error((log10(Biomass))), MeanMeanAggSize = mean(MeanAggSize), SEMeanAggSize = std.error(MeanAggSize))

#Get aggregate Summary per condition and region
aggregateListSummaryCondition<-aggregateListSummaryReplicate %>% group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region) %>% summarise(MeanAggs= mean(Aggs), MeanBiomassLog = mean(log10(Biomass)), SEBiomassLog = std.error((log10(Biomass))), MeanMeanAggSize = mean(MeanAggSize), SEMeanAggSize = std.error(MeanAggSize))
```
```{r Overview Plots}
#Plot agg summary per sample
#####
ggplot()+ 
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Strain,shape = "MeanSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Strain, shape = "MaxSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Strain, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(Species~Culture, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  scale_color_brewer(palette = "Set1")+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
#####
#Plot only biomass per Sample
#####
PlotBiomasPerSample<-function(df){
ggplot()+ 
    #this is for multiple conditions
  #geom_point(data = df, aes(x = Strain, y= biomass, shape = Region, color = Culture),size = 3, position = position_dodge(width = .6))+
  geom_point(data = df, aes(x = Culture, y= biomass, color= Species, shape = Region),size = 3, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
      #this is for multiple conditions  
    #facet_grid(Species~TimePoint, scales = "free", space = "free") +
    #this is for only one mutant
    facet_grid(.~TimePoint, scales = "free", space = "free") +
  ggtitle('Total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(1, 2,0))+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

@@

#There are two ways to normalize the Bin Frequncy and Bin Biomass, per condition and per sample, so I'll do both
#First per replicate:
#####
HistReplicate<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ "(.5, 5]",
                        Size<= 10 ~ "(5, 10]",
                        Size<= 100    ~ "(10, 100]",
                        Size<= 1000   ~ "(100, 1000]",
                        Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
  group_by(SampleCode,Species)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% 
  group_by(SampleCode,Species,LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

@@

#This is weird, but I want to have the histogram above with all the data, and the one below with only the bins
HistReplicateSummary<-HistReplicate %>% 
  group_by(SampleCode,Species,SaStrain,Strain,Culture,TimePoint,Condition,Replicate,Region,LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%
  unique()%>%ungroup() %>%  group_by(SampleCode,Species,SaStrain,Strain,Culture,TimePoint,Condition,Replicate,Region) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
#####
#Now per condition. The difference is int the "group_by" part
#####
HistCondition<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ "(.5, 5]",
                        Size<= 10 ~ "(5, 10]",
                        Size<= 100    ~ "(10, 100]",
                        Size<= 1000   ~ "(100, 1000]",
                        Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
  group_by(Species,Condition,TimePoint)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% 
  group_by(Species,Condition,TimePoint,LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)
HistCondition$LogBin <- factor(HistCondition$LogBin, levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")")),labels = c(levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")"))))

#Summary data frame
HistConditionSummary<-HistCondition %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
  summarize() %>% unique()%>%ungroup() %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
#####

#Now per condition including region. The difference is int the "group_by" part
#####
HistConditionRegin<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ "(.5, 5]",
                        Size<= 10 ~ "(5, 10]",
                        Size<= 100    ~ "(10, 100]",
                        Size<= 1000   ~ "(100, 1000]",
                        Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
  group_by(Species,Condition,TimePoint,Region)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>%
  group_by(Species,Condition,TimePoint,Region,LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

HistConditionRegin$LogBin <- factor(HistConditionRegin$LogBin, levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")")),labels = c(levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")"))))
#Summary data frame
HistCondRegionSum<-HistConditionRegin %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
  summarize() %>% unique()%>%ungroup() %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
#####
```

```{r Plot Aggregate size bins}
#Plot Normalized Frequency
#this isn't useful as the normalized Frequency changes with replicate, so it's better to pool all samples together
PlotHistSum<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4")%>% filter(Species == species),
                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4")%>% filter(Species == species),
               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=3, position = position_dodge(width = .75) )+
    geom_point(data = cond.df%>% filter(TimePoint=="Day 4") %>% filter(Species == species),
               aes(x=as.factor(LogBin),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~Species)+
    scale_shape_manual(values=c(16, 1))+
    ggtitle(title)+
    labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotHistSum(HistReplicateSummary,HistConditionSummary,HistCondRegionSum,"NormalizedFrequency", "Normalized Frequency all sizes", "S. aureus")

@@

PlotHistSum(HistReplicateSummary%>% filter(Culture =="co"),
            HistConditionSummary%>% filter(Culture =="co"),
            HistCondRegionSum%>% filter(Culture =="co"),
            "NormalizedFrequency", "Normalized Frequency all sizes", "P. aeruginosa", "Strain")

#Plot normalized Biomass per sample
##Pa
PlotHistRepBioTrend<-function(rep.df,species){
ggplot()+
    geom_line(data = rep.df %>% filter(Species==species),aes(x=as.factor(LogBin),y=NormalizedBiomass, color = Replicate, group = Replicate ),size=1)+
    guides(color = FALSE)+
    facet_grid(Condition~TimePoint)+
    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    ggtitle(paste('Normalized Biomass per Sample', species))+
    theme_cowplot()+
    scale_colour_grey()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5)) }
PlotHistRepBioTrend(HistReplicateSummary, "P. aeruginosa")
PlotHistRepBioTrend(HistReplicateSummary, "S. aureus")
```

```{Aggregates Only, Not currently in use}
#####
#Now only aggregates 5 microns or larger

@@

#####
```
```{r Aggregates vs Planktonics}
#Planktonic vs aggregates
#####
#Add agregation value to the dataframe 
##Normalize using replicates
HistReplicate<-HistReplicate %>%  mutate(Aggregation = if_else(LogBin == "(.5, 5]" ,"Planktonic", "Aggregate")) %>%
  group_by(Species,SampleCode, Aggregation)%>% 
  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
#Collapse to only values per replicate
plankAggHistRep<-HistReplicate %>% 
  group_by(SampleCode,Species,SaStrain,Strain,Culture,TimePoint,Condition,Replicate,Region,Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% 
  summarize() %>%  unique()%>%ungroup() %>%  
  group_by(SampleCode,Species,SaStrain,Strain,Culture,TimePoint,Condition,Replicate,Region) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))

##Normalize using Condition 
HistCondition<-HistCondition %>%  mutate(Aggregation = if_else(LogBin == "(.5, 5]", "Planktonic", "Aggregate")) %>%
  group_by(Species,Condition,TimePoint,Aggregation)%>% 
  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
#Collapse to only values per replicate
plankAggHistCond<-HistCondition %>% 
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>%
  summarize() %>%  unique()%>%ungroup() %>%  
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))

##Normalize using Condition and region
HistConditionRegin<-HistConditionRegin %>%  mutate(Aggregation = if_else(LogBin == "(.5, 5]", "Planktonic", "Aggregate")) %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region,Aggregation)%>% 
  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
#Collapse to only values per condition and Replicate
plankAggHistCondReg<-HistConditionRegin %>% 
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region,Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>%
  summarize() %>%  unique()%>%ungroup() %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
```

```{r Plot Aggregate vs planktonics}

#Plot Frequency
PlotAggPlank<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain, facet){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4")%>% filter(Species == species),
                aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4")%>% filter(Species == species),
               aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=3, position = position_dodge(width = .75) )+
    geom_point(data = cond.df%>% filter(TimePoint=="Day 4") %>% filter(Species == species),
               aes(x=as.factor(Aggregation),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c(16, 1))+
    ggtitle(title)+
    labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
###---Figure 1D
PlotAggPlank(plankAggHistRep%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
             plankAggHistCond%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
             plankAggHistCondReg%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
             "AgPlNormBiomass", "Normalized Biomass", "S. aureus", "Culture", "Species")

PlotAggPlank(plankAggHistRep,
             plankAggHistCond,
             plankAggHistCondReg,
             "AgPlNormBiomass", "Normalized Biomass", "S. aureus", "SaStrain","Species")

PlotAggPlank(plankAggHistRep,
             plankAggHistCond,
             plankAggHistCondReg,
             "AgPlNormBiomass", "Normalized Biomass", "P. aeruginosa", "Strain","Culture")

#Plot Biomass
ggplot()+
  geom_jitter(data = plankAggHistRep,
              aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition ),size=2, height = 0, width = .2, shape = 1)+
  geom_point(data = plankAggHistCond,
             aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition),size=5, shape = 16, position = position_dodge2(width = .5)) +
  facet_grid(Species~TimePoint)+
  ggtitle("Normalized Biomass (%) Aggs vs Plank")+
  labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+ 
  theme_cowplot()+
  panel_border() +
  scale_color_brewer(palette = "Set1")+
  theme(plot.title = element_text(hjust = 0.3)) 
#####
```
